A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-09 paper/ms.tex
update ms

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Radial velocities acquired using Keck/HIRES during the
    transit of 2021 Aug 7, observed simultaneously with MuSCAT3.}
    Shaded bands show 2-$\sigma$ model uncertainties.  The photometric
    transit depths are consistent across the {\it griz} bandpasses.
    The best-fitting model in the top panel includes the RM effect and
    a quadratic trend in time to model the spot-induced
    $\approx$\,$250$\ms\ trend (see Appendix~\ref{app:rm}).  The
    radial velocity jitter over the 15~minute exposure timescale
    ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
    effect.  The RV variations are strongly correlated with varying
    emission in the Ca H and K lines (middle panel).
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar density
and TTV-local slope correlation.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations may also
show a transit duration $17.3\pm4.0\ {\rm minutes}$ shorter than the
Kepler transits; further photometric follow-up would help confirm
whether the transit duration is indeed changing.  For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.74\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater precision should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations aimed at quantifying the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  The most feasible
approach would likely be long-term monitoring of the transit times and
durations, given the technical difficulty of performing a multi-color
radial velocity campaign on a $V=13$ star.  Measured at
sufficient precision though, the mass, combined with the known age and
size, would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

@@

\clearpage
\acknowledgements
\raggedbottom

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f7.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Keck/HIRES radial velocities and MuSCAT3 photometry from the transit of 2021 Aug 7.}
    {\it Top:} 
    The radial velocity jitter across the 15~minute exposures
    ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
    effect;
    a model including the RM anomaly and a quadratic trend in time to
    fit the spot-induced $\approx$\,$250$\ms\ trend is shown (see
    Appendix~\ref{app:rm}).  Shaded bands show 2-$\sigma$ model
    uncertainties.  
    {\it Middle:} The RV variations are strongly correlated with varying
    emission in the Ca H and K lines.
    {\it Bottom}: The photometric transit depths are consistent across
    the {\it griz} bandpasses. The photometry is binned at 10~minute
    intervals.
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar density
and TTV-local slope correlation.  We observed a transit of \pn\ on the
night of 2021 Aug 7 simultaneously with Keck/HIRES and MuSCAT3.  We
scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting the MuSCAT3
photometry with a model that lets the transit depths vary across each
bandpass, we find {\it griz} depths consistent with the Kepler depth
at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  Conditioned on the
Kepler ephemeris and transit depth, the MuSCAT3 observations may also
suggest a transit duration $17.3\pm4.3\ {\rm minutes}$ shorter than the
Kepler transits; further photometric follow-up could help confirm
whether the transit duration is indeed changing.  For our RM analysis,
the details are discussed in Appendix~\ref{app:rm}.  While the
velocities are marginally more consistent with a prograde or polar
orbit than a retrograde orbit, the spot-corrected exposure-to-exposure
scatter ($\sigma_{\rm RV}\approx 30$\ms) is comparable to the expected
RM anomaly assuming an aligned orbit ($\Delta v_{\rm RM}\approx
20\,{\rm m\,s}^{-1}$).  We are therefore not in a position to claim a
spectroscopic detection of the RM effect, nor to quantify the stellar
obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.8\textwidth]{f8.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
    3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
    its uncertainty.  \pn\ is shown with a star.  The large sizes of
    the youngest transiting planets could be explained by their
    primordial atmospheres not yet having evaporated; direct
    measurements of the atmospheric outflows or planetary masses would
    help to confirm this expectation.  Selection effects may also be
    important.  Parameters are from the NASA Exoplanet Archive (2021
    Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

Kepler\,1627Ab provides a new extremum in the ages of the Kepler
planets, and opens multiple avenues for further study.  Observations
of spectroscopic transits at greater precision should yield a
measurement of the stellar obliquity, which would confirm or refute
the prograde orbital geometry suggested by the TTV-local slope
correlation.  Separately, transit spectroscopy aimed at detecting
atmospheric outflows could yield insight into the evolutionary state
of the atmosphere \citep[{\it
e.g.},][]{ehrenreich_giant_2015,spake_helium_2018,vissapragada_2020}.
Observations that quantify the amount of high-energy
irradiation incident on the planet would complement these efforts, by
helping to clarify the expected outflow rate \citep[{\it
e.g.},][]{poppenhaeger_2021}.  Finally, a challenging but informative
quantity to measure would be the planet's mass.  The most feasible
approach would likely be long-term monitoring of the transit times and
durations, given the technical difficulty of performing a multi-color
radial velocity campaign on a $V=13$ star.  Measured at
sufficient precision though, the mass, combined with the known age and
size, would yield constraints on both the planet's composition and its
initial entropy \citep{owen_constraining_2020}.

@@

% \clearpage
\acknowledgements
\raggedbottom
